The NIME of the Title Is Hello

### 2025-01-16 src/main.tex
Updates from Overleaf

%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
To Robert, for the bagels and explaining CMYK and color spaces.
\end{acks}

>>>>

%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
A project of this breadth developed across 3 institutes and 2 countries
cannot be carried without the support and technical knowledge of many
skilled and passionate people.

We acknowledge the invaluable contributions of

\begin{itemize}
\tightlist
\item
  Unibo

  \begin{itemize}
  \tightlist
  \item
    Alma Labor

    \begin{itemize}
    \tightlist
    \item
      Massimiliano Fraulini and the staff of Alma Labor at the Yiversità
      of bologna for their 3D printing expertise and generosity with
      electronics equipment
    \end{itemize}
  \item
    Fisica Tecnica

    \begin{itemize}
    \tightlist
    \item
      Maurzio Chendi Fabrizio Casarini, Giulio Severo and Barbara
      Costantini
    \end{itemize}
  \end{itemize}
\item
  San Colombano

  \begin{itemize}
  \tightlist
  \item
    Catalina Vincens
  \item
    Roberto Livi
  \end{itemize}
\item
  Edinburgh

  \begin{itemize}
  \tightlist
  \item
    uCreate

    \begin{itemize}
    \tightlist
    \item
      Simeon, Stuart, Millie, and Ruth of uCreate at the Univeristy of
      Edinburgh for their support with soldering facilities.
    \end{itemize}
  \item
    ECA

    \begin{itemize}
    \tightlist
    \item
      Richard Collins and the Digital Making Staff at the Edinburgh
      College of Art for 3D printing instruction and CNC support.
    \item
      Joe Hathaway of Digital Development at the College of Art for
      providing electronics components
    \item
      St Cecilia's Jenny Nex
    \end{itemize}
  \end{itemize}
\end{itemize}
\end{acks}
